Accelerated oblique random survival forests

### 2022-06-20 docs/index.Rmd
tidying up plotly results

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 100,
  fig.align='center',
  fig.height=5
)

@@

A total of 23 risk prediction tasks in 16 data sets were analyzed.

@@

- For each of the 23 risk prediction problems,

@@

Step 2: Fit a hierarchical Bayesian model to analyze posterior expected differences in performance:

$$\text{metric} = \widehat{\gamma} \cdot \text{model} + (1\,|\, \text{data/run})$$

@@

fig <- plot_ly(width = 800, height = 650) %>%
  add_trace(
    type = 'bar',
    x = fig_data$pred_corr_max,
    y = fig_data$overall,
    color = fig_data$model,
    text = table_value(fig_data$overall),
    textposition = 'outside',
    hoverinfo = 'text',
    hovertext = fig_data$text
  ) %>%
  plotly::layout(
    title = list(text = 'Results when N = 1000', x = 0.1),
    xaxis = list(title = 'Max correlation among predictors'),
    yaxis = list(title = 'C-statistic'),
    legend = list(title = list(text = '<b>VI technique</b>'))
  )

@@

fig <- plot_ly(width = 800, height = 650) %>%
  add_trace(
    type = 'bar',
    x = fig_data$pred_corr_max,
    y = fig_data$overall,
    color = fig_data$model,
    text = table_value(fig_data$overall),
    textposition = 'outside',
    hoverinfo = 'text',
    hovertext = fig_data$text
  ) %>%
  plotly::layout(
    title = list(text = 'Results when N = 5000', x = 0.1),
    xaxis = list(title = 'Max correlation among predictors'),
    yaxis = list(title = 'C-statistic'),
    legend = list(title = list(text = '<b>VI technique</b>'))
  )

@@

A total of 23 risk prediction tasks in 16 data sets were analyzed.

This table is continued on the next 2 slides.

@@

tbls <- data_key |> 
  select(label, outcome, nrow, ncol, nevent, pcens, pmiss, pctns) |> 
  mutate(
    across(starts_with('p'),  ~.x * 100),
    across(where(is.numeric), .fns = table_value),
    outcome = Hmisc::capitalize(outcome)
  ) |> 
  arrange(label) |> 
  mutate(grp = seq(n()),
         grp = case_when(
           grp > 2 * n()/3 ~ 3, 
           grp > 1 * n()/3 ~ 2,
           TRUE ~ 1
         )) |> 
  group_by(grp) |> 
  group_map(
    ~ .x |> 
      gt(rowname_col = 'label') |> 
      cols_label(
        outcome = 'Outcome',
        nrow = 'N Obs',
        ncol = 'N Predictors',
        nevent = 'N Events',
        pcens = '% Censored',
        pmiss = '% Missing',
        pctns = "% Continuous"
      ) |> 
      cols_align(align = 'center') |> 
      cols_align(align = 'left', columns = 'outcome')
  )

@@

>>>>

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 600,
  fig.align='center',
  fig.height=5
)

@@

A total of 31 risk prediction tasks in 18 data sets were analyzed.

@@

- For each of the 31 risk prediction problems,

@@

Step 2: Fit a Bayesian linear mixed model to analyze posterior expected differences in performance:

$$\text{metric} = \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run})$$

@@

fig <- plot_ly(width = 800, height = 650) %>%
  add_trace(
    type = 'bar',
    x = fig_data$pred_corr_max,
    y = fig_data$overall,
    color = fig_data$model,
    colors = "PuRd",
    text = table_value(fig_data$overall),
    textposition = 'outside',
    hoverinfo = 'text',
    hovertext = fig_data$text
  ) %>%
  plotly::layout(
    title = list(text = 'Results when N = 1000', x = 0.1),
    xaxis = list(title = 'Max correlation among predictors'),
    yaxis = list(title = 'C-statistic', range = c(0,1)),
    legend = list(title = list(text = '<b>VI technique</b>'))
  )

@@

fig <- plot_ly(width = 800, height = 650) %>%
  add_trace(
    type = 'bar',
    x = fig_data$pred_corr_max,
    y = fig_data$overall,
    color = fig_data$model,
    colors = "PuRd",
    text = table_value(fig_data$overall),
    textposition = 'outside',
    hoverinfo = 'text',
    hovertext = fig_data$text
  ) %>%
  plotly::layout(
    title = list(text = 'Results when N = 5000', x = 0.1),
    xaxis = list(title = 'Max correlation among predictors'),
    yaxis = list(title = 'C-statistic', range = c(0,1)),
    legend = list(title = list(text = '<b>VI technique</b>'))
  )

@@

A total of 31 risk prediction tasks in 18 data sets were analyzed.

This table is continued on the next 3 slides.

@@

tbls <- data_key |> 
  select(label, outcome, nrow, ncol, nevent, pcens, pmiss, pctns) |> 
  mutate(
    across(starts_with('p'),  ~.x * 100),
    across(where(is.numeric), .fns = table_value),
    outcome = Hmisc::capitalize(outcome)
  ) |> 
  arrange(label) |> 
  mutate(grp = seq(n()),
         grp = case_when(
           grp > 3 * n()/4 ~ 4,
           grp > 2 * n()/4 ~ 3, 
           grp > 1 * n()/4 ~ 2,
           TRUE ~ 1
         )) |> 
  group_by(grp) |> 
  group_map(
    ~ .x |> 
      gt(rowname_col = 'label') |> 
      cols_label(
        outcome = 'Outcome',
        nrow = 'N Obs',
        ncol = 'N Predictors',
        nevent = 'N Events',
        pcens = '% Censored',
        pmiss = '% Missing',
        pctns = "% Continuous"
      ) |> 
      cols_align(align = 'center') |> 
      cols_align(align = 'left', columns = 'outcome')
  )

@@

tbls[[4]]
